APPM 3310 Project\\\Large{Static Analysis of Truss Systems}

### 2016-04-25 paper.tex
Add Introduction from Sammy Chang.

\section{Introduction}

>>>>

\section{Introduction}
The truss analyzer implements the DSM by simplifying and idealizing a given
truss system. By that, all of the joints are converted to frictionless pin
joins, and we will ignore the bending of individual truss members. Our
idealization for most cases is satisfactory for an elementary truss analysis.
Therefore we will only be observing the axial forces and the displacements at
the pin joints. Our truss analyzer "converts" the pins and members to a node
and an element, respectively under the Cartesian coordinate system.
Furthermore, we are able to apply external forces only at the joints. This
will allow us to simulate displacement in all the nodes of the truss system.
The analyzer works by inputting a truss system, the code then identifies
individual elements. When the elements are identified, the truss system is
disassembled at the nodes. The elements are further analyzed using stiffness
equations dependent on the geometry and the elastic moduli of the elements.
Once those elements have been analyzed, the code re-assembles the structure
with the stiffness of the elements. The element stiffness matrix is then
modified by applying the displacements and externally applied forces at the
nodes. A final matrix is obtained (global stiffness matrix) which can be
solved using the displacement and force vectors by applying the Cholesky
decomposition. Using DSM allows us to analyze complex truss structures as well
as statically indeterminate structures.
